A weighted sampling algorithm to designing RNA sequences with target secondary structure and nucleotide distribution

### 2013-01-08 ISMB/introduction_ISMB.tex

Most of RNA functions are, at least partially, encoded by the three-dimensional molecular structures, which are themselves primarily determined by the secondary structures. The development of efficient algorithms for designing RNA sequences with pre-defined secondary structures is thus a milestone to enter the synthetic biology era. \RNAinverse pioneered RNA secondary structure design algorithms. It has been developed and distributed with the Vienna RNA package \cite{Hofacker:1994}. However, only posterior experimental studies revealed the potential and practical impact of these techniques. Thereby, during the last 6 years many improvements and variants of \RNAinverse have been proposed. Conceptually, almost all of existing algorithms follow the same approach. First a seed sequence is selected, then a local search strategy is used to mutate the seed and find, in its vicinity, a sequence with desired folding properties. Using this strategy, \INFORNA \cite{Busch:2006uq}, \RNASSD \cite{Aguirre-Hernandez:2007kx} and \NUPACK \cite{Zadeh:2011fk} significantly improved the performance of RNA secondary structure design algorithms. More recent research studies aimed to include more constraints in the selection criteria.\RNAexinv focused on the design of sequences with enhanced thermodynamical and mutational robustness \cite{Avihoo:2011fk}, while \frankenstein enables to design RNA with multiple target structures \cite{Lyngso:2012vn}.

>>>>

Most of RNA functions are, at least partially, encoded by the three-dimensional molecular structures, which are themselves primarily determined by the secondary structures. The development of efficient algorithms for designing RNA sequences with pre-defined secondary structures is thus a milestone to enter the synthetic biology era. \RNAinverse pioneered RNA secondary structure design algorithms. It has been developed and distributed with the Vienna RNA package \cite{Hofacker:1994}. However, only posterior experimental studies revealed the potential and practical impact of these techniques. Thereby, during the last 6 years many improvements and variants of \RNAinverse have been proposed. Conceptually, almost all of existing algorithms follow the same approach. First a seed sequence is selected, then a local search strategy is used to mutate the seed and find, in its vicinity, a sequence with desired folding properties. Using this strategy, \INFORNA \cite{Busch:2006uq}, \RNASSD \cite{Aguirre-Hernandez:2007kx} and \NUPACK \cite{Zadeh:2011fk} significantly improved the performance of RNA secondary structure design algorithms. More recent research studies aimed to include more constraints in the selection criteria. \RNAexinv focused on the design of sequences with enhanced thermodynamical and mutational robustness \cite{Avihoo:2011fk}, while \frankenstein enables to design RNA with multiple target structures \cite{Lyngso:2012vn}.
